Data Exploration

### 2021-11-29 code/analysis_code/analysis_uown.Rmd
Include References & Formatting - CC

### Required packages
```{r}
library(tidyverse) #Working with multiple Tidy packages
library(tidymodels) #Building models
library(dplyr) #data manipulation
library(here) #setting pathways for saving files
library(rpart) #Model fitting
library(ranger) #Model fitting
library(glmnet) #Model fitting
library(knitr) #saving tables
```

@@

_Outcome: Biological Score_
```{r}
#Creates a dataframe that stores the cook's distance analysis of influential data points.
bs_con_cd <- cooks.distance(bs_con_lm)
plot(bs_con_cd, pch="*", cex=2, main="MIDO: Conductivity vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

bs_ecfu_cd <- cooks.distance(bs_ecfu_lm)
plot(bs_ecfu_cd, pch="*", cex=2, main="MIDO: E. coli CFU vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

bs_no3_cd <- cooks.distance(bs_no3_lm)
plot(bs_no3_cd, pch="*", cex=2, main="MIDO: NO3 vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

bs_turb_cd <- cooks.distance(bs_turb_lm)
plot(bs_turb_cd, pch="*", cex=2, main="MIDO: Turbidity vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")
```
</br>
_Outcome: E.coli CFU_
```{r}
#Creates a dataframe that stores the cook's distance analysis of influential data points.
ecfu_con_cd <- cooks.distance(ecfu_con_lm)
plot(ecfu_con_cd, pch="*", cex=2, main="MIDO: Conductivity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

@@

ecfu_turb_cd <- cooks.distance(ecfu_turb_lm)
plot(ecfu_turb_cd, pch="*", cex=2, main="MIDO: Turbidity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_MIDO, col="red")
```
</br>

@@

</br>
_Outcome: Biological Score_
```{r}
#Creates a dataframe that stores the cook's distance analysis of influential data points.
n_bs_con_cd <- cooks.distance(n_bs_con_lm)
plot(n_bs_con_cd, pch="*", cex=2, main="NORO: Conductivity vs. Biological Score with Outliers")
abline(h = 4/sample_size_NORO, col="red")

@@

n_bs_turb_cd <- cooks.distance(n_bs_turb_lm)
plot(n_bs_turb_cd, pch="*", cex=2, main="NORO: Turbidity vs. Biological Score with Outliers")
abline(h = 4/sample_size_NORO, col="red")
```
</br>

_Outcome: E.coli CFU_
```{r}
#Creates a dataframe that stores the cook's distance analysis of influential data points.
n_ecfu_con_cd <- cooks.distance(n_ecfu_con_lm)
plot(n_ecfu_con_cd, pch="*", cex=2, main="NORO: Conductivity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_NORO, col="red")

@@

n_ecfu_turb_cd <- cooks.distance(n_ecfu_turb_lm)
plot(n_ecfu_turb_cd, pch="*", cex=2, main="NORO: Turbidity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_NORO, col="red")
```
</br>

@@

_Outcome: Biological Score_
```{r}
#Creates a dataframe that stores the cook's distance analysis of influential data points.
b_bs_con_cd <- cooks.distance(b_bs_con_lm)
plot(b_bs_con_cd, pch="*", cex=2, main="BICO: Conductivity vs. Biological Score with Outliers")
abline(h = 4/sample_size_BICO, col="red")

@@

b_bs_turb_cd <- cooks.distance(bs_turb_lm)
plot(b_bs_turb_cd, pch="*", cex=2, main="BICO: Turbidity vs. Biological Score with Outliers")
abline(h = 4/sample_size_BICO, col="red")
```
</br>

_Outcome: E.coli CFU_
```{r}
#Creates a dataframe that stores the cook's distance analysis of influential data points.
b_ecfu_con_cd <- cooks.distance(b_ecfu_con_lm)
plot(b_ecfu_con_cd, pch="*", cex=2, main="BICO: Conductivity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_BICO, col="red")

@@

b_ecfu_turb_cd <- cooks.distance(b_ecfu_turb_lm)
plot(b_ecfu_turb_cd, pch="*", cex=2, main="BICO: Turbidity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_BICO, col="red")
```
</br>

@@

#### Save significant Test and Train linear models to the results folder.
```{r}
#Create a table for E. coli (cfu) as a function of Conductivity Linear Fit Model in the MIDO train data.
MIDO_ECFU_Con_fit <- kable(as.tibble(Ecoli_con_lm),
      caption = "Linear Fit Model: E. Coli CFU predicted by Conductivity in the Trained MIDO Data Set")

MIDO_ECFU_Con_fit

@@

#### Save significant Test and Train RMSE to the results folder.
```{r}
#Create a table for E. coli (cfu) as a function of Conductivity Linear Fit Model RMSE in the MIDO train data.
MIDO_ECFU_Con_RMSE <- kable(as.tibble(Ecoli_con_RMSE),
      caption = "Root Mean Square Error: E. Coli CFU predicted by Conductivity in the Trained MIDO Data Set")

MIDO_ECFU_Con_RMSE

@@

Null_Met <- kable(Null_Met,
      caption = "Root Mean Squared Error and Standard Deviation for Biological Score Null Linear Model")

Null_Met
```
_RMSE = 6.63, with a standard deviation of 0.13. This will serve as our check to test our models against latter on._

@@

Best_LASSO_BS <- kable(top_five_bs,
      caption = "Top 5 best performing LASSO Models for Biological Score as the Outcome")

Best_LASSO_BS
```

@@

Null_Met_EC <- kable(Null_Met_EC,
      caption = "Root Mean Squared Error and Standard Deviation for E. coli cfu Null Linear Model")

Null_Met_EC
```
_RMSE = 0.52, with a standard deviation of 0.014. This will serve as our check to test our models against latter on._

@@

Best_LASSO_EC <- kable(top_five_ec,
      caption = "Top 5 best performing LASSO Models for E. coli cfu as the Outcome")

Best_LASSO_EC
```

>>>>

### Required packages
```{r}
library(tidyverse) #working with multiple Tidy packages
library(tidymodels) #building models
library(dplyr) #data manipulation
library(here) #setting pathways for saving files
library(rpart) #model fitting
library(ranger) #model fitting
library(glmnet) #model fitting
library(knitr) #saving tables
library(gridExtra) #grouping figure outputs together
```

@@

_Outcome: Biological Score_
```{r, fig.width=10}
#Set save file path parameters
png(filename = here::here("results", "MIDO_BS_OUT.png"), width = 10, height = 6, units = "in", res = 300)

par(mfrow=c(2,2)) #group plots together using base r

#Creates a dataframe that stores the cook's distance analysis of influential data points.
bs_con_cd <- cooks.distance(bs_con_lm)
bs_con_cd_plot <- plot(bs_con_cd, pch="*", cex=2, main="MIDO: Conductivity vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

bs_ecfu_cd <- cooks.distance(bs_ecfu_lm)
bs_ecfu_cd_plot <- plot(bs_ecfu_cd, pch="*", cex=2, main="MIDO: E. coli CFU vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

bs_no3_cd <- cooks.distance(bs_no3_lm)
bs_no3_cd_plot <- plot(bs_no3_cd, pch="*", cex=2, main="MIDO: NO3 vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

bs_turb_cd <- cooks.distance(bs_turb_lm)
bs_turb_cd_plot <- plot(bs_turb_cd, pch="*", cex=2, main="MIDO: Turbidity vs. Biological Score with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

dev.off()
```
</br>
_Outcome: E.coli CFU_
```{r, fig.width=10}
#Set save file path parameters
png(filename = here::here("results", "MIDO_EC_OUT.png"), width = 10, height = 6, units = "in", res = 300)

par(mfrow=c(2,2)) #group plots together using base r

#Creates a dataframe that stores the cook's distance analysis of influential data points.
ecfu_con_cd <- cooks.distance(ecfu_con_lm)
plot(ecfu_con_cd, pch="*", cex=2, main="MIDO: Conductivity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

@@

ecfu_turb_cd <- cooks.distance(ecfu_turb_lm)
plot(ecfu_turb_cd, pch="*", cex=2, main="MIDO: Turbidity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_MIDO, col="red")

dev.off()
```
</br>

@@

</br>
_Outcome: Biological Score_
```{r, fig.width=10}
#Set save file path parameters
png(filename = here::here("results", "NORO_BS_OUT.png"), width = 10, height = 6, units = "in", res = 300)

par(mfrow=c(2,2)) #group plots together using base r

#Creates a dataframe that stores the cook's distance analysis of influential data points.
n_bs_con_cd <- cooks.distance(n_bs_con_lm)
plot(n_bs_con_cd, pch="*", cex=2, main="NORO: Conductivity vs. Biological Score with Outliers")
abline(h = 4/sample_size_NORO, col="red")

@@

n_bs_turb_cd <- cooks.distance(n_bs_turb_lm)
plot(n_bs_turb_cd, pch="*", cex=2, main="NORO: Turbidity vs. Biological Score with Outliers")
abline(h = 4/sample_size_NORO, col="red")

dev.off()
```
</br>

_Outcome: E.coli CFU_
```{r, fig.width=10}
#Set save file path parameters
png(filename = here::here("results", "NORO_EC_OUT.png"), width = 10, height = 6, units = "in", res = 300)

par(mfrow=c(2,2)) #group plots together using base r

#Creates a dataframe that stores the cook's distance analysis of influential data points.
n_ecfu_con_cd <- cooks.distance(n_ecfu_con_lm)
plot(n_ecfu_con_cd, pch="*", cex=2, main="NORO: Conductivity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_NORO, col="red")

@@

n_ecfu_turb_cd <- cooks.distance(n_ecfu_turb_lm)
plot(n_ecfu_turb_cd, pch="*", cex=2, main="NORO: Turbidity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_NORO, col="red")

dev.off()
```
</br>

@@

_Outcome: Biological Score_
```{r, fig.width=10}
#Set save file path parameters
png(filename = here::here("results", "BICO_BS_OUT.png"), width = 10, height = 6, units = "in", res = 300)

par(mfrow=c(2,2)) #group plots together using base r

#Creates a dataframe that stores the cook's distance analysis of influential data points.
b_bs_con_cd <- cooks.distance(b_bs_con_lm)
plot(b_bs_con_cd, pch="*", cex=2, main="BICO: Conductivity vs. Biological Score with Outliers")
abline(h = 4/sample_size_BICO, col="red")

@@

b_bs_turb_cd <- cooks.distance(bs_turb_lm)
plot(b_bs_turb_cd, pch="*", cex=2, main="BICO: Turbidity vs. Biological Score with Outliers")
abline(h = 4/sample_size_BICO, col="red")

dev.off()
```
</br>

_Outcome: E.coli CFU_
```{r, fig.width=10}
#Set save file path parameters
png(filename = here::here("results", "BICO_EC_OUT.png"), width = 10, height = 6, units = "in", res = 300)

par(mfrow=c(2,2)) #group plots together using base r

#Creates a dataframe that stores the cook's distance analysis of influential data points.
b_ecfu_con_cd <- cooks.distance(b_ecfu_con_lm)
plot(b_ecfu_con_cd, pch="*", cex=2, main="BICO: Conductivity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_BICO, col="red")

@@

b_ecfu_turb_cd <- cooks.distance(b_ecfu_turb_lm)
plot(b_ecfu_turb_cd, pch="*", cex=2, main="BICO: Turbidity vs. E. coli CFU with Outliers")
abline(h = 4/sample_size_BICO, col="red")

dev.off()
```
</br>

@@

#### Save significant Test and Train linear models to the results folder.
```{r}

#Create a table for E. coli (cfu) as a function of Conductivity Linear Fit Model in the MIDO train data.
MIDO_ECFU_Con_fit <- kable(as.tibble(Ecoli_con_lm),
      caption = "Table 1: Linear Fit Model: E. Coli CFU predicted by Conductivity in the Trained MIDO Data Set")

MIDO_ECFU_Con_location <- here::here("results", "MIDO_ECFU_Con_location.RDS")

saveRDS(MIDO_ECFU_Con_fit, MIDO_ECFU_Con_location)

@@

#### Save significant Test and Train RMSE to the results folder.
```{r}
#Create a table for E. coli (cfu) as a function of Conductivity Linear Fit Model RMSE in the MIDO train data.
MIDO_ECFU_Con_RMSE <- kable(as.tibble(Ecoli_con_RMSE),
      caption = "Table 2: Root Mean Square Error: E. Coli CFU predicted by Conductivity in the Trained MIDO Data Set")

MIDO_ECFU_Con_RMSE_location <- here::here("results", "MIDO_ECFU_Con_RMSE_location.RDS")

saveRDS(MIDO_ECFU_Con_RMSE, MIDO_ECFU_Con_RMSE_location)

@@

Null_Met <- kable(Null_Met,
      caption = "Table 3: Root Mean Squared Error and Standard Deviation for Biological Score Null Linear Model")

BS_Null_Mod_Location <- here::here("results", "BS_Null_Mod_Location.RDS")

saveRDS(Null_Met, BS_Null_Mod_Location)
```
_RMSE = 6.63, with a standard deviation of 0.13. This will serve as our check to test our models against latter on._

@@

Best_LASSO_BS <- kable(top_five_bs,
      caption = "Table 4: Top 5 best performing LASSO Models for Biological Score as the Outcome")

Best_LASSO_BS_location <- here::here("results", "Best_LASSO_BS_location.RDS")

saveRDS(Best_LASSO_BS, Best_LASSO_BS_location)
```

@@

Null_Met_EC <- kable(Null_Met_EC,
      caption = "Table 5: Root Mean Squared Error and Standard Deviation for E. coli cfu Null Linear Model")

Null_Met_EC_location <- here::here("results", "Null_Met_EC_location.RDS")

saveRDS(Null_Met_EC, Null_Met_EC_location)
```
_RMSE = 0.52, with a standard deviation of 0.014. This will serve as our check to test our models against latter on._

@@

Best_LASSO_EC <- kable(top_five_ec,
      caption = "Table 6: Top 5 best performing LASSO Models for E. coli cfu as the Outcome")

Best_LASSO_EC_location <- here::here("results", "Best_LASSO_EC_location.RDS")

saveRDS(Best_LASSO_EC, Best_LASSO_EC_location)
```

### 2021-11-29 code/processing_code/Data_Exploration.Rmd
Include References & Formatting - CC

#### First, we need to load all the libraries we will need.
```{r}
library(dplyr) 
library(here)
library(tidyverse)
library(tidyr)
library(readr)
library(stringr)
library(gridExtra)
```

>>>>

#### First, we need to load all the libraries we will need.
```{r}
library(dplyr) #data manipulation
library(here) #setting pathways for saving files
library(tidyverse) #Working with multiple Tidy packages
library(tidyr) #data cleaning
library(readr) #read in files
library(stringr) #working with strings
library(gridExtra) #grouping figure outputs together
```
